Application of Machine Learning to Predict the Optoelectronic Properties of Benzobisazoles

### 2014-11-22 paper/paper.tex
Update paper
Add a small update to the paper

Overall, the support vector machines with Gaussian kernel had the best performance across all of the machine learning methods and all of the feature vectors. This matches similarly to the results seen in \hl{.... [CITE]}; however, they found that the Laplacian kernel performed the best. The suspected reason for the difference in the two results is thought to be because the method used in that study involved single atoms as features, whereas this method was dealing with entire functional groups. The smoothness of the gaussian distribution is probably a better estimator in that (especially with something like a phenyl ring). For the SVM with Gaussian kernel, the optimized hyperparameters to be $C \approx 10$ and $\gamma \approx 0.05$ for all of the properties.

@@

>>>>

Overall, the support vector machines with Gaussian kernel had the best performance across all of the machine learning methods and all of the feature vectors. This matches similarly to the results seen in \hl{.... [CITE]}\cite{hansen_assessment_2013}; however, they found that the Laplacian kernel performed the best. The suspected reason for the difference in the two results is thought to be because the method used in that study involved single atoms as features, whereas this method was dealing with entire functional groups. The smoothness of the gaussian distribution is probably a better estimator in that (especially with something like a phenyl ring). For the SVM with Gaussian kernel, the optimized hyperparameters to be $C \approx 10$ and $\gamma \approx 0.05$ for all of the properties.

@@

Upon doing PCA on the binary feature vectors, it can be seen that the weights/influence for each of the substituents is directly related to its Hammet parameter value.
